{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-26 draft.tex

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition on
execution of individual KCFs. To minimize the effect of drifting, we
developed a re-detection module that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
69.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 3\% on AUC on average. Our implementation
ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
faster than DCF (292 fps) for OTB100.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition on
execution of individual KCFs. To minimize the effect of drifting, we
developed a re-detection module that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
72.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}
